\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.7in, bottom=0.3in]{geometry} % Adjusted bottom margin
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{multicol}

\titleformat{\section}
  {\Large\bfseries\color{blue}}
  {}{0em}
  {}[\titlerule]

\pagestyle{empty}

\begin{document}

\vspace*{-2cm}

\begin{center}
\Huge\textbf{Ian De Holanda Cavalcanti Bezerra}

\LARGE Applied Mathematics and Computer Science Student

\large\href{mailto:idhcb.ian@usp.br}{idhcb.ian@usp.br}
\end{center}

\section*{Profile}
\vspace{-0.5em}
\begin{multicols}{2}
\setlength{\columnsep}{0.4cm}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.15em}
\normalsize

I'm an Applied Math and Computer Science Student at ICMC USP. I am passionate about working on hard problems and building the future. In university, I developed a keen interest in AI and computer science. Mainly, the use of smarter systems to push the frontier of human knowledge greatly interests me! I'm a firm believer in efficiency and simplicity; fast execution and iterative improvements can achieve great things.

Since childhood, I've been fascinated by science and technology. In middle school, I created the Pong game using Scratch, and in high school, I delved deeper into computers and systems, learning Python and Linux. Recognizing the fundamental importance of mathematics in understanding reality and intelligent systems, I chose to pursue Applied Mathematics and Computer Science at the University of São Paulo.

At university, I've expanded my knowledge of data structures, algorithms, and lower-level programming systems like C and Assembly. My side projects explore artificial intelligence and modern Neural Network architectures. Recently, I've become interested in the commercial aspects of programming, learning web technologies like HTML/CSS/JavaScript and frameworks such as Node.js and React to turn intelligent systems and algorithms into products.
\end{multicols}
\vspace{-0.5em}

\section*{Education}
\vspace{-0.5em}
\begin{itemize}[leftmargin=*, itemsep=-1.5pt]
  \item \textbf{Colégio Bandeirantes} - São Paulo
    \begin{itemize}[itemsep=-1pt]
      \item Graduated: 2021
    \end{itemize}
  \item \textbf{Bachelor's in Applied Mathematics and Computer Science}
    \begin{itemize}[itemsep=-1pt]
      \item University of São Paulo (USP), São Carlos
      \item Expected Graduation: 2026
    \end{itemize}
\end{itemize}
\vspace{-0.5em}

\section*{Skills}
\vspace{-0.5em}
\begin{itemize}[leftmargin=*, itemsep=-1.5pt]
  \item Programming Languages (Proficient): Python, C
  \item Programming Languages (Basic): Assembly, Rust
  \item Web Development: HTML, CSS, JavaScript, React, Node.js, D3.js
  \item Data Analysis: MATLAB, SQL
  \item Python Libraries: PyTorch, Numpy, Matplotlib, Pandas, Multiprocessing
  \item Infrastructure: AWS (EC2, Amplify, S3, APIGateway), Docker, Git
  \item Linux (Highly proficient)
  \item Math background: Numerical Analysis, Probability, and Optimization.
\end{itemize}
\vspace{-0.5em}

\section*{Projects and Experiences}
\vspace{-0.5em}
\begin{itemize}[leftmargin=*, itemsep=-1.5pt]
  \item Member of the coding extension group CodeLab
  \item Developed a PyTorch AI for organic molecule classification
  \item University of São Paulo: Scientific Initiation Project on graph visualization of Neural Network embeddings and semi-supervised learning with Graph Convolutional Networks.
  \item BrickLugo: Developed an Airbnb pricing model and the Startup's website (Frontend and Backend).
  \item Personal website with portfolio and side projects: \href{https://iansmainframe.com}{iansmainframe.com}
\end{itemize}
\vspace{-0.5em}

\section*{Languages}
\vspace{-0.5em}
\begin{itemize}[leftmargin=*, itemsep=-1.5pt]
  \item Portuguese (Native)
  \item English (Fluent)
\end{itemize}

\end{document}
